SVG: The Paper

### 2022-04-14 Analysis/index.Rmd
some mini tidying

ggplot(a_cut, aes(b_bin, acc, colour = condition, shape = condition)) + 
  geom_point() + 
  geom_line(stat = "smooth", method = "loess", 
            formula = y ~ x, alpha = 0.65, size = 2, se = F) +
  geom_abline(linetype = 2) +
  scale_x_continuous("largest item weight") +
  scale_y_continuous("proportion of times selected") + 
  coord_fixed()
```

@@

plts[[1]] + plts[[2]] +
  plot_layout(nrow = 1, widths = c(1,1)) &
   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8"))
```

>>>>

ggplot(a_cut, aes(b_bin, acc, colour = condition, shape = condition)) + 
  geom_point() + 
  geom_line(stat = "smooth", method = "loess", 
            formula = y ~ x, alpha = 0.65, size = 2, se = F) +
  geom_abline(linetype = 2) +
  scale_x_continuous("largest item weight") +
  scale_y_continuous("proportion of times selected") #+ 
  #coord_fixed()
```

@@

plts[[1]] + plts[[2]] +
  plot_layout(nrow = 1, widths = c(1,1)) &
   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8")) &
   theme(text=element_text(size=14,  family="serif"))
```
